---
title: "Does Perceived Job Insecurity Affect Mental Health? Evidence from the 2021 Chinese General Social Survey"
author: "Team Kish"
header-includes:
    - \usepackage{setspace}
    - \usepackage{longtable}
    - \usepackage{booktabs}
    - \usepackage{siunitx}
output: 
  pdf_document:
    latex_engine: xelatex
linestretch: 1
geometry: margin = 1in
fontsize: 11pt
mainfont: Times New Roman
bibliography: references.bib
csl: asa.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE,
                      eval = TRUE)
```

```{r packages and data, include=FALSE}
library(tidyverse)
library(lavaan)
library(gtsummary)
library(survey)
library(knitr)
library(kableExtra)
## the following package needs to be installed manually
## because it is not available on CRAN
## some other dependencies may be required, follow the instructions
library(semTable)

load("FinalResults.RData")
```

# Introduction

With rising global competition, industrial shifts, and economic recessions, an increasing number of employees face concerns about layoffs. The instability and unpredictability of labor markets impose significant psychological burdens on workers, often resulting in adverse health outcomes linked to job insecurity. Understanding the relationship between job insecurity and health is crucial for informing interventions aimed at improving workers' well-being. Previous research has established a connection between perceived job insecurity and poor health outcomes. After accounting for demographic, socioeconomic, and job characteristics, as well as prior health conditions, perceived job insecurity was found associated with deteriorating health among U.S. workers [@burgard_perceived_2009]. Similarly, McDonough [-@mcdonough_job_2000], using a national sample of Canadian adults, reported that high levels of job insecurity lead to lower self-rated health, increased psychological distress, and increased use of medication for symptom relief.

This study investigates the impact of perceived job insecurity on self-rated mental health using data from the 2021 Chinese General Social Survey (CGSS), a nationally representative sample. Employing structural equation modeling, we examine the relationship between the latent construct of perceived job insecurity and various measures of mental well-being. We hypothesize that perceived job insecurity will be negatively associated with these mental well-being indicators, suggesting potential detrimental effects of perceived job insecurity on psychological health measures. 

H1: Perceived job insecurity will be negatively associated with self-rated mental health.

H2: Perceived job insecurity will be negatively associated with self-rated mental health among different

H3: Perceived job insecurity will be negatively associated with self-rated mental health among different

# Data and Methods

## Data

CGSS

## Measures

job insecurity: how to measure, 5; 

mental health: how to measure, 3; 

control variables: which variables, 2;

## Analytical approach

model; estimator: "WLSMV", why?; which parameter (coeffient); MGA: how to do, which statistics?

# Results

## Descriptive statistics

```{r descriptive statistics, results='asis'}
CGSS2 = CGSS %>% 
  mutate(workhours = as.numeric(workhours),
         workcontract = as.factor(workcontract),
         workself = as.factor(workself),
         satisfaction = as.factor(satisfaction),
         workstress = as.factor(workstress),
         depressed = as.factor(depressed),
         happy = as.factor(happy),
         health = as.factor(health),
         sex = as.factor(sex),
         party = as.factor(party)) %>% 
  mutate(workcontract = recode(workcontract, 
                          "1" = "Infinite Term", 
                          "2" = "Fixed Term", 
                          "3" = "No Contract"),
         workself = recode(workself, "1" = "Completely Controlled By Self",
                            "2" = "Mainly Controlled By Self",
                            "3" = "Mainly Controlled By Others",
                            "4" = "Completely Controlled By Others"),
         satisfaction = recode(satisfaction, "1" = "Very Satisfied", 
                               "2" = "Satisfied", 
                               "3" = "Neutral", 
                               "4" = "Dissatisfied", 
                               "5" = "Very Dissatisfied"),
         workstress = recode(workstress, "1" = "Rarely", 
                             "2" = "Sometimes", 
                             "3" = "Often", 
                             "4" = "Always"),
         depressed = recode(depressed, "1" = "Always", 
                            "2" = "Often", 
                            "3" = "Sometimes", 
                            "4" = "Rarely", 
                            "5" = "Never"),
         happy = recode(happy, "1" = "Never", 
                        "2" = "Rarely", 
                        "3" = "Sometimes", 
                        "4" = "Often", 
                        "5" = "Always"),
         health = recode(health, "1" = "Always", 
                         "2" = "Often", 
                         "3" = "Sometimes", 
                         "4" = "Rarely",
                         "5" = "Never"))

design = svydesign(id = ~1, weights = ~weight, data = CGSS2)

descriptive = design %>% 
  tbl_svysummary(
    include = c(workhours, workcontract, workself, satisfaction, 
                workstress, depressed, happy, health, sex, party),
    digits = list(all_continuous() ~ 2, all_categorical() ~ 1),
    statistic = list(all_continuous() ~ "{mean} ({sd})",
                     all_categorical() ~ "{p}%"),
    type = list(workhours ~ "continuous",
                c(workcontract, workself, satisfaction, workstress, depressed, happy, health, sex, party) ~ "categorical"),
    label = list(
      workhours = "Weekly work hours",
      workcontract = "Type of work contract",
      workself = "Work autonomy",
      satisfaction = "Job satisfaction",
      workstress = "Work stress",
      depressed = "Feel depressed",
      happy = "Feel happy",
      health = "Health affects work/daily life",
      sex = "Sex",
      party = "Party membership"
  ) 
) %>% 
  modify_header(
    label ~ "**Variable**",
    all_stat_cols() ~ "Mean (SD) / Percent") %>% 
  modify_footnote(everything() ~ NA) %>% 
  modify_caption("Weighted descriptive statistics (N = 993)") %>%
  bold_labels()

as_kable_extra(descriptive, format = "latex", booktabs = TRUE, longtable = TRUE)
```

## Job insecurity and mental health

```{r H1 result, results='asis'}
semTable(
  object = c(" " = fit1),
  type = "latex",
  longtable = TRUE,
  paramSets = c("loadings", "slopes", "fits"),
  caption = "Structural equation model results for the
         relationship between perceived job insecurity and mental
         health",
  varLabels = c(
    "insecurity" = "Perceived job insecurity",
    "mental" = "Mental health",
    "workhours" = "Weekly work hours",
    "workcontract" = "Type of work contract",
    "workself" = "Work autonomy",
    "satisfaction" = "Job satisfaction",
    "workstress" = "Work stress",
    "depressed" = "Feel depressed",
    "happy" = "Feel happy",
    "health" = "Health affects work/daily life"
  )
)
```


## job insecurity and mental health among different sex categories

```{r H2 result, results='asis'}
semTable(
  object = c(" " = fit2_sex),
  type = "latex",
  longtable = TRUE,
  paramSets = c("loadings", "slopes", "fits"),
  caption = "Structural equation model results for the
         relationship between perceived job insecurity and mental
         health among different sex categories",
  columns = c("eststars", "se"),
  alpha = c(0.1, 0.05, 0.01),
  varLabels = c(
    "insecurity" = "Perceived job insecurity",
    "mental" = "Mental health",
    "workhours" = "Weekly work hours",
    "workcontract" = "Type of work contract",
    "workself" = "Work autonomy",
    "satisfaction" = "Job satisfaction",
    "workstress" = "Work stress",
    "depressed" = "Feel depressed",
    "happy" = "Feel happy",
    "health" = "Health affects work/daily life"
  )
)
```

## job insecurity and mental health among different party memberships

# References


